Drones in Wind

### 2017-07-26 Papers/DroneInTheWind.tex
Analysis

\section{Goal}
The "Drones in Wind" simulation simulates the flight of a quadcopter drone. The drone in the simulation will be modeled after the AscTec Pelican, a research-drone by the German company Ascending Technologies. The simulated drone as of the point of writing this paper is equipped with sensors to measure the velocity in the horizontal and vertical axis, the vertical position and the pitch angle. The goal is to create a controller that linearizes about a trajectory given by the third-party program OptimTraj. The trajectory comes from a cost function that minimizes the time integral of error from a desired position.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                                 Model                                                                                  %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Model}
The motion of the drone is governed by the ordinary differential equations with the state defined as
\begin{equation}
\label{state}
x = \begin{bmatrix} x\\ \dot{x} \\ z \\ \dot{z} \\ \theta \end{bmatrix}
\end{equation}
such that $x$, $z$, correspond to horizontal and vertical position, respectively, and $\theta$ corresponds to the angle of the quad from upright. The inputs for the system are defined as
\begin{equation}
\label{inputs}
u = \begin{bmatrix} \omega \\ f \end{bmatrix}
\end{equation}
such that $\omega$ corresponds to angular pitch rate and $f$ corresponds to thrust. Taking the Jacobian lends the following A and B matrices shown by Equation \ref{A_matrix_intermediate} and Equation \ref{B_matrix_intermediate}
\begin{equation}
\label{A_matrix_intermediate}
A = \begin{bmatrix} 0 && 1 && 0 && 0 && 0 \\ 0 && 0 && 0 && 0 && \frac{f\cos{\theta}}{m} \\  0 && 0 && 0 && 1 && 0 \\ 0 && 0 && 0 && 0 && \frac{-f\sin{\theta}}{m} \\ 0 && 0 && 0 && 0 && 0 \end{bmatrix}
\end{equation}

@@

\begin{flushleft}
{\Large \textbf{\textbf{Solution}} }
\end{flushleft}
Finally, to solve, the command \lstinline!soln = optimTraj(problem)! is run. You can then unpack the simulation, save the data, and plot out
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                                Analysis                                                                                %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Analysis}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                                Future Work                                                                         %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Future Work}
With the completion of a 2D optimized drone path, plans to enhance the simulation are underway. Several additions will be added to the current simulation in order to complete this task. Those are as follows 
\newline
\begin{itemize}
  \item Implement 3D rigid body dynamics
  \item Implement additional aerodynamic forces such as drag and ground effect
\end{itemize}
With these immediate goals in mind, an accurate simulation can be created to further test the overarching research initiative.
% Display list of references in IEEE Transactions format.
\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,references}

>>>>

\section{Goal}
The "Drones in Wind" simulation simulates the flight of a quadcopter drone. The drone in the simulation will be modeled after the AscTec Pelican, a research-drone by the German company Ascending Technologies. The simulated drone as of the point of writing this paper is equipped with sensors to measure the velocity in the horizontal and vertical axis, the vertical position and the pitch angle. The goal is to create a controller that linearizes about a trajectory given by the third-party program OptimTraj. The trajectory comes from a cost function that minimizes the time integral of error from a desired position.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                                 Model                                                                                  %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Model}
The motion of the drone is governed by the ordinary differential equations with the state defined as
\begin{equation}
\label{state}
x = \begin{bmatrix} x\\ \dot{x} \\ z \\ \dot{z} \\ \theta \end{bmatrix}
\end{equation}
such that $x$ and $z$ correspond to horizontal and vertical position, respectively, while $\theta$ corresponds to the angle of the quad from upright. The inputs for the system are defined as
\begin{equation}
\label{inputs}
u = \begin{bmatrix} \omega \\ f \end{bmatrix}
\end{equation}
such that $\omega$ corresponds to angular pitch rate and $f$ corresponds to thrust. Taking the Jacobian lends the following A and B matrices shown by Equation \ref{A_matrix_intermediate} and Equation \ref{B_matrix_intermediate}
\begin{equation}
\label{A_matrix_intermediate}
A = \begin{bmatrix} 0 && 1 && 0 && 0 && 0 \\ 0 && 0 && 0 && 0 && \frac{f\cos{\theta}}{m} \\  0 && 0 && 0 && 1 && 0 \\ 0 && 0 && 0 && 0 && \frac{-f\sin{\theta}}{m} \\ 0 && 0 && 0 && 0 && 0 \end{bmatrix}
\end{equation}

@@

\begin{flushleft}
{\Large \textbf{\textbf{Solution}} }
\end{flushleft}
Finally, to solve, the command \lstinline!soln = optimTraj(problem)! is run. You can then unpack the simulation, save the data, and plot out
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                                Analysis                                                                                %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Analysis}
A method that computes quadcopter trajectories satisfying the minimal principle with respect to time-optimality has been developed. The method is based on the two-dimensional quadcopter model with an optimal trajectory created using OptimTraj. By defining the dynamics, bounds and cost function the algorithm was able to create an optimal path for which the drone was to follow. Testing this method, the simulated drone accomplished moving from a position (0,0) to (1,1) in a time optimal manner.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                                Future Work                                                                         %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Future Work}
With the completion of a 2D optimized drone path, plans to enhance the simulation are underway. Several additions will be added to the current simulation in order to complete this task. Those are as follows 
\newline
\begin{itemize}
  \item Implement 3D rigid body dynamics
  \item Implement additional aerodynamic forces such as drag and ground effect
\end{itemize}
With these immediate goals in mind, an accurate simulation can be created to further test the overarching research initiative.
% Display list of references in IEEE Transactions format.
\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,references}
